A self-consistency check for unitary propagation of Hawking quanta

### 2016-11-02 Draft_BH_shells.tex

\begin{abstract}
The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
We establish an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT is related to the soft-hair-memory effect.
\end{abstract}

>>>>

\begin{abstract}
The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
We establish an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT might be related to the soft-hair-memory effect.
\end{abstract}
